Fail Faster

### 2025-03-18 paper/paper.tex
Tiny comment

\section{Sources of Inefficiency in Monadic Generator Libraries}
\label{section:motiv}
\jwc{In this section we answer: ``What are monadic generator libraries, and why are they slow?''}

@@

All experiments were run on a 64-bit Linux machine with 264 GB RAM and an Intel Xeon Platinum 8375C CPU, running Ubuntu 24.04.1 LTS.
The \name library was implemented using the
4.14.1+BER MetaOCaml compiler variant.  All OCaml benchmarks
were run invoking \texttt{ocamlopt}, the native code compiler for OCaml, using compiler flags \texttt{-flamda -o3}.

>>>>

\section{Sources of Inefficiency in Monadic Generator Libraries}
\label{section:motiv}
\jwc{In this section we answer: ``What are monadic generator libraries, and why are they slow?''}
\bcp{That's actually not a bad section title!}

@@

All experiments were run on a 64-bit Linux machine with 264 GB RAM and an Intel Xeon Platinum 8375C CPU, running Ubuntu 24.04.1 LTS.
The \name library was implemented using the
4.14.1+BER MetaOCaml compiler variant.  All OCaml benchmarks
were run invoking \texttt{ocamlopt}, the native code compiler for OCaml, using compiler flag \texttt{-O3}.
